\malg: a novel interest management algorithm for distributed simulations of MMOGs

### 2008-05-07 textos/dsrt/engaoi.tex
refs para AOI

In the past few years, many works have been done trying to distribute the network support for massively multiplayer online games. One approach is the peer-to-peer model, which has some issues concerning game state consistency among the participating peers, vulnerability to cheating, and increased bandwidth usage by each peer. There are some proposals that try to minimize these problems. One of them is presented in \cite{schiele2007rpp}, where it is suggested the division of the virtual simulated game environment into regions, and for each region, a peer is chosen to be its coordinator. The function of this peer will be manage the players' interest. It will check who really needs each state update, so each player does not receive every update packet. This way, the peers' bandwidth usage is reduced. However, it will be still higher than with a server performing all the broadcasts. In the peer-to-peer model, each player usually must send updates to more than one other player. Besides, the chosen peer must be trustable to be the region coordinator.

@@

A key problem in the peer-to-peer architectures, in what concerns the use of interest management, is that some peers are responsible for part of the simulation and for decide to whom each state update interests. Assuming that there are only trustable players, the interest management technique may be useful. However, supposing that a player is malicious, he could hack his client software and avoid sending state updates to certain players, who would be in disadvantage. Consequently, the distributed server model is considered more suitable to use the interest management technique.

@@

This work is based on a virtual environment partitioned into regions, each managed by a different server. The regions are contiguous, exploring the locality of the players' avatars. Thus, avatars next to each other will probably be located in the same region and, therefore, their clients will tend to be connected to the same server, so that their interaction is faster (Fig. \ref{partitions}). Situations in which two players interacting with each other are connected to different servers imply a higher bandwidth usage, as it is required some sort of negotiation between the servers to which the different players are connected, in order to maintain the states of the simulation identical in both servers. Also, the hop count of each message between the clients of these players is increased, since there is one more intermediary.

@@

In the previous sections, we have hinted that filtering based on an avatar field of view of 180 degrees (for instance) instead of using a full circle around it could result in significant reduction in update traffic from the server to the avatar player's machine. However, that would bring an important drawback, which is the large but temporary inconsistencies that would ensue whenever a player would turn around his avatars quickly to see what remotely-controlled objects are behind it. We have also reminded that reducing update frequencies for objects that are farther away from an avatar is a good optimization, especially for large virtual worlds where it may be on an open field with potentially hundreds of other avatars in its sighting distance. In this case, the player will not benefit at all from receiving updates at maximum frequency from objects that are sufficiently distant.
%from using the maximum update frequency that is granted to objects that are at maximum closeness to the player being updated.

>>>>

In the past few years, many works have been done trying to distribute the network support for massively multiplayer online games. One approach is the peer-to-peer model \cite{endo2005dam, hampel2006ppa, knutsson2004pps}, which has some issues concerning game state consistency among the participating peers, vulnerability to cheating, and increased bandwidth usage by each peer. There are some proposals that try to minimize these problems. One of them is presented in \cite{schiele2007rpp}, where it is suggested the division of the virtual simulated game environment into regions, and for each region, a peer is chosen to be its coordinator. The function of this peer will be manage the players' interest. It will check who really needs each state update, so each player does not receive every update packet. This way, the peers' bandwidth usage is reduced. However, it will be still higher than with a server performing all the broadcasts. In the peer-to-peer model, each player usually must send updates to more than one other player. Besides, the chosen peer must be trustable to be the region coordinator.

@@

A key problem in the peer-to-peer architectures, in what concerns the use of interest management, is that some peers are responsible for part of the simulation and for decide to whom each state update interests. Assuming that there are only trustable players, the interest management technique may be useful. However, supposing that a player is malicious, he could hack his client software and avoid sending state updates to certain players, who would be in disadvantage. Consequently, the distributed server model \cite{assiotis2006dam, ng2002msa, fiedler2002cam, rieche2007ppb}  is considered more suitable to use the interest management technique.

@@

This work is based on a virtual environment partitioned into regions, each managed by a different server. The regions are contiguous, exploring the locality of the players' avatars. Thus, avatars next to each other will probably be located in the same region and, therefore, their clients will tend to be connected to the same server, so that their interaction is faster (Figure \ref{partitions}). Situations in which two players interacting with each other are connected to different servers imply a higher bandwidth usage, as it is required some sort of negotiation between the servers to which the different players are connected, in order to maintain the states of the simulation identical in both servers. Also, the hop count of each message between the clients of these players is increased, since there is one more intermediary.

@@

In the previous sections, we have hinted that filtering based on an avatar field of view of 180 degrees, for instance, instead of using a full circle around it could result in significant reduction in update traffic from the server to the avatar player's machine. However, that would bring an important drawback, which is the large but temporary inconsistencies that would ensue whenever a player would turn around his avatars quickly to see what remotely-controlled objects are behind it. We have also reminded that reducing update frequencies for objects that are farther away from an avatar is a good optimization, especially for large virtual worlds where it may be on an open field with potentially hundreds of other avatars in its sighting distance. In this case, the player will not benefit at all from receiving updates at maximum frequency from objects that are sufficiently distant.
%from using the maximum update frequency that is granted to objects that are at maximum closeness to the player being updated.
